Secure Composition of Robust and Optimising Compilers

### 2023-06-29 popl/main.tex
Ltms
pos
Add Ltms example

>>>>

\begin{lstlisting}[language=c,basicstyle=\small\ttfamily, caption=C]
int strncpy(int n, int *x, int *y) {
  for(int i = 0; x[i] != '\0' && i < n; ++i) {
    y[i] = x[i];
  }
}
\end{lstlisting}

\begin{lstlisting}[language=ml,basicstyle=\small\ttfamily,morekeywords={ifz}, caption=$\Ltms$]
let strncpy p : int * int * ptr int * ptr int -> ptr int * ptr int :=
  let [i, n, x, y] = p in
  ifz x[i] then
    ifz i < n then
      return call strncpy (i+1, n, x, y)
    else
      return (x, y)
  else
    return (x, y)
\end{lstlisting}
